\section{Selected Projects}
\cvSubHeadingListStart

%---------------------------------------------------------
\cvProjectHeading
{\textbf{Real--Time Feedback for Upper-Limb Motor Rehabilitation Using AR}
 $|$ \emph{\href{https://github.com/mustafizur-r/arposetrainerapp-live}{GitHub}}}
{\Csharp{} $|$ Unity $|$ REST API}
\cvItemListStart
\cvItem{Developed an AR-based upper-limb rehabilitation system using Azure Kinect and Microsoft HoloLens.}
\cvItem{Implemented skeletal tracking and UDP/IP communication for real-time avatar visualization.}
\cvItem{Provided pose assessment and real-time performance feedback for therapists and patients.}
\cvItemListEnd

\clearpage

%---------------------------------------------------------
\cvProjectHeading
{\textbf{Handwrite AI: OCR for Handwritten Note Digitization}}
{Python $|$ PyTorch $|$ FastAPI}
\cvItemListStart
\cvItem{Developed an OCR application that converts scanned handwritten notes into editable and searchable digital text.}
\cvItem{Implemented deep-learning-based handwriting recognition to support different handwriting styles.}
\cvItem{Designed the system to facilitate document digitization and information retrieval.}
\cvItemListEnd

%---------------------------------------------------------
\cvProjectHeading
{\textbf{AI-Based Signature Authentication System}}
{Python $|$ PyTorch $|$ Image Processing}
\cvItemListStart
\cvItem{Developed an AI-based signature authentication system using image-processing and machine-learning techniques.}
\cvItem{Implemented automated signature verification and forgery detection.}
\cvItem{Improved document authentication reliability through biometric signature analysis.}
\cvItemListEnd

\cvSubHeadingListEnd