\section{Peer-reviewed Conference}

\cvJournalListStart
\cvJournal
{\textbf{Md Mustafizur Rahman}$^{*}$, Goshiro Yamamoto, Chang Liu, Hiroaki Ueshima, Isidro Butaslac, Taishi Sawabe, and Hirokazu Kato.}
{Generating Patient-Specific Abnormal Gait Motions for Therapists’ Observational Skill Training}
{International Journal of Activity and Behavior Computing (IJABC), J-STAGE}
{accept as a POSITION Paper}
{}
{}
{}
{}
\cvJournalListEnd


\cvConfListStart
\cvConference
{Mariolino De Cecco$^{*}$, Giandomenico Nollo, Alessandro Luchetti, Matteo Bonetto, Damiano Fruet, Muhammad Irtaza, \textbf{Md Mustafizur Rahman}$^{*}$, Ryosuke Shigeto, Isidro Butaslac}
{Robotic Collaborative Walker with Impedance Control and Augmented Reality for Assisted Walking and User Empowerment}
{2025 IEEE International Conference on Metrology for eXtended Reality, Artificial Intelligence and Neural Engineering (MetroXRAINE)}
{ANCONA, Italy}
{October. 2025}
{pp. 1367–1372}
{https://doi.org/10.1109/MetroXRAINE66377.2025.11340234}
{10.1109/MetroXRAINE66377.2025.11340234}

\cvConference
{\textbf{Md Mustafizur Rahman}$^{*}$, Goshiro Yamamoto, Chang Liu, Hiroaki Ueshima, Isidro Butaslac, Taishi Sawabe, and Hirokazu Kato.}
{Experience Augmentation in Physical Therapy by Simulating Patient-Specific Walking Motions}
{16th Asia-Pacific Workshop on Mixed and Augmented
Reality (APMAR 2024)}
{Kyoto, Japan}
{Nov. 2024}
{vol 3907}
{https://ceur-ws.org/Vol-3907/paper12.pdf}
{[paper link]}

\cvConference
{\textbf{Md. Mustafizur Rahman}$^{*}$, Md Fatin Ishmam, Md. Tanvir Hossain, Md. Emdadul Haque}
{Virtual Reality Based Medical Training Simulator and Robotic Operation System}
{2022 International Conference on Recent Progresses in Science, Engineering and Technology (ICRPSET)}
{Rajshahi, Bangladesh}
{December 2022}
{pp. 1-4}
{https://doi.org/10.1109/ICRPSET57982.2022.10188546}
{[10.1109/ICRPSET57982.2022.10188546]}

\cvConfListEnd

%-------------------------
% \section{Workshop Publications}

% \cvWorkshopListStart
% \cvConference
% {\textbf{I. Butaslac}, A. Luchetti, J. Ino, Y. Fujimoto, T. Sawabe, M. Kanbara, H. Kato, K. Uemura, Y. Otake, Y. Sato, M. Takao, and N. Sugano}
% {Application of Participatory Design Methodology in AR: Developing Prototypes for Two Context Scenarios}
% {2022 IEEE International Symposium on Mixed and Augmented Reality Adjunct, W12: Design and User Research in AR/VR/MR}
% {Singapore}
% {Oct. 2022}
% {pp. 244--248}
% {https://ieeexplore.ieee.org/document/9974297}
% {10.1109/ISMAR-Adjunct57072.2022.00054}

% \cvConference
% {A. Luchetti, \textbf{I. Butaslac}, M. Rosi, D. Fruet, G. Nollo, P. Ianes, F. Pilla, B. Gasperini, G. Guandalini, J. Bonavita, H. Kato, and M. De Cecco}
% {Multidimensional assessment of daily living activities in a shared Augmented Reality environment}
% {2022 IEEE International Workshop on Metrology for Living Environment}
% {Cosenza, Italy}
% {May 2022}
% {pp. 60--65}
% {https://ieeexplore.ieee.org/document/9826952}
% {10.1109/metrolivenv54405.2022.9826952}

% \cvConference
% {M. Abe, T. Akiyoshi, \textbf{I. Butaslac}, H. Zhou, and T. Sawabe}
% {Hype Live: Biometric-based Sensory Feedback for Improving the Sense of Unity in VR Live Performance}
% {2022 IEEE Conference on Virtual Reality and 3D User Interfaces Abstracts and Workshops}
% {Christchurch, New Zealand}
% {Mar. 2022}
% {pp. 836--837}
% {https://ieeexplore.ieee.org/document/9757560}
% {10.1109/vrw55335.2022.00269}
% \cvWorkshopListEnd