\section{Experiences}
\cvSubHeadingListStart
\cvSubheading{Kyoto University Hospital}{March 2024 -- Present}{Visiting Researcher $|$ Prof. Goshiro Yamamoto}{Kyoto, Japan}

\cvItemListStart

\cvItem{Collaborating with professors Goshiro Yamamoto, Chang Liu, and Hiroaki Ueshima from the Clinical Research Center for Medical Equipment Development.}

\cvItem{Involved in multidisciplinary projects focused on optimizing rehabilitation practices in physical therapy settings.}

\cvItem{Engaged in research titled "Generating Patient-Specific Abnormal Gait Motions for Therapists’
Observational Skill Training" enhancing rehabilitation outcomes through advanced simulation techniques.}
\cvItemListEnd
%---
\cvSubheading{University of Trento }{March 2025 -- May 2025}{Visiting Researcher, \href{https://www.miro.ing.unitn.it/}{MiRo Lab} $|$ Prof. Mariolino De Cecco}{Trento, Italy}

\cvItemListStart

\cvItem{Completed a research internship under the supervision of Professor Mariolino De Cecco and Alessandro Luchetti, PhD at MiroLab , focusing on the development of Mixed Reality systems for industrial and rehabilitation applications.}

\cvItem{Developed a mixed-reality based serious game on HMD, integrating a collaborative robotic walker with a spatially aware AR interface.}

\cvItem{Validated the system through co-location between therapist and patient HMDs, synchronized with an external robotic walker to support adaptive gait rehabilitation.}

\cvItemListEnd

%---
\cvSubheading
  {SQA Engineer Lead $|$ Talent Pro}
  {June 2022 -- August 2023}
  {Team Lead for \href{https://realezy.com/}{Real Ezy Pte. Ltd., Singapore}}
  {Dhaka, Bangladesh}

\cvItemListStart

\cvItem{Led QA automation initiatives and improved testing efficiency across multiple projects.}

\cvItem{Designed and maintained automation frameworks with Selenium WebDriver, Appium, TestNG, and Cucumber (TDD/BDD).}

\cvItem{Developed and executed automated test scripts, ensuring high coverage and reliability.}

\cvItem{Performed API automation with REST Assured and GraphQL, plus performance, security, and database testing.}

\cvItem{Analyzed test results and collaborated with developers to quickly identify and resolve defects, enhancing product quality.}

\cvItemListEnd

%---
% \cvSubheading{Nara Institute of Science and Technology}{September 2023 -- Present}{Research Assistant, \href{http://imd.naist.jp/}{IMD Lab} $|$ Prof. Hirokazu Kato}{Nara, Japan}

% \cvItemListStart

% \cvItem{Served as a \Csharp{}/Unity developer creating VR games ({\hyperref[sec:VR Photo Studio]{\underline{VR Photo Studio}} and \href{https://www.dropbox.com/s/zfha1npr9ypn324/OCimd.mp4?dl=0}{\underline{Virtual Castell}}}) for open campus, indirectly boosting the lab's profile and contributing to the enrollment of 16 new students for 2022 and 2023.}

% \cvItem{Developed a smartphone interface to complement HoloLens 2's hand gesture input, simplifying AR 3D object manipulation for beginners with buttons, sliders, and virtual joysticks for seamless smartphone\texttt{--}HoloLens interaction.}

% \cvItemListEnd

%---


\cvSubHeadingListEnd
